Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-19 paper/manuscript.Rmd
update msc

```{r tab-model-comparison}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>% 
  dplyr::filter(formula != "formula_full") %>%
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
   knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their Wanatabe-Akaike information criterion (WAIC).") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
```

>>>>

```{r tab-model-comparison}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>% 
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::filter(formula != "formula_full") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
  knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their Wanatabe-Akaike information criterion (WAIC).") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
```
